Determining the alternatives for scalar implicature

### 2016-01-27 Paper/Paper.Rmd
minor tweaks before meeting with MF 1.27.16

$$ p_{S_1} (u \mid m) \propto p_{L_0} (m \mid u)$$

@@

$$p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}$$

@@

In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT). In the two-alternative condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded \footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials. We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,1c} for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants. In the four-alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants. In the five-alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.

@@

Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank. Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" They were prompted to generate three unique alternatives.

@@

Experiment 3 was conducted to measure pragmatic judgments $p_{L_1}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014. We include two conditions in Experiment 3. In the two-alternative entailment condition, participants made judgments for items included in the entailment scales. In the four-alternative condition, participants made pragmatic judgments for the entialment items and also the top two alternatives elicited for each scale in Experiment 2. Running two pragmatic judgment conditions allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions. \footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

We recruited 100 participants from AMT, 50 for each condition. Data for `r 50 - length(unique(exp3a$workerid))` participants in the two-alternative condition were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of `r length(unique(exp3a$workerid))` participants. In the four-alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp3b$workerid))` participants.

@@

To test whether there were between experiment differences in pragmatic judgments, we ran a mixed effects model, regressing pragmatic judgements on scale and experiment with subject and word level random effects. Results indicate there were no significant differences between Experiment 3a and 3b for $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 2)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.

@@

Using literal semantic data from Experiment 1 we conducted three simulations with our model. Each simulation used the specific literal semantic data to specify the scale representation available to our model. The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014). These data were measured in Experiment 1a. The "Top two" model extended the original set of alternatives with the top two alternatives generated in Experiment 2. These data were measured in Experiment 3a. The "Full" model included the full set of alternatives, including a neutral valenced alternative. These data were measured in Experiment 4.

>>>>

$$ p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)$$

@@

$$p_{S_1}(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}$$

@@

In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT). In the two-alternative condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded \footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials. We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,c} for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants. In the four-alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants. In the five-alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.

@@

Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank. Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.

@@

Experiment 3 was conducted to measure pragmatic judgments $p_{L_1}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014. We include two conditions in Experiment 3. In the two-alternative condition, participants made judgments for items included in the entailment scales. In the four-alternative condition, participants made judgments for the entialment items and also the top two alternatives elicited for each scale in Experiment 2. Running two pragmatic judgment conditions allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions. \footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

We recruited 100 participants from AMT, 50 for each condition. Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants. In the four-alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp3b$workerid))` participants.

@@

To test whether there were between experiment differences in pragmatic judgments, we ran a mixed effects model, regressing pragmatic judgements on scale and experiment with subject and word level random effects. Results indicate there were no significant differences between Experiment 3a and 3b for $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.

@@

Using literal semantic data from Experiments 1a,b,c we conducted three simulations with our model. Each simulation used the specific literal semantic data to specify the scale representation available to our model. The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014). These data were measured in Experiment 1a. The "Top two" model extended the original set of alternatives with the top two alternatives generated in Experiment 2. These data were measured in Experiment 3a. The "Full" model included the full set of alternatives, including a neutral valenced alternative. These data were measured in Experiment 4.

### 2016-01-27 Paper/Paper.tex
minor tweaks before meeting with MF 1.27.16

\[ p_{S_1} (u \mid m) \propto p_{L_0} (m \mid u)\]

@@

\[p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}\]

@@

In each condition we recruited 30 participants from Amazon Mechanical
Turk (AMT). In the two-alternative condition, 16 participants were
excluded
\footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials. We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,1c}
for either failing to pass two training trails or were not native
English speakers, leaving a total sample of 14 participants. In the
four-alternative condition, 7 participants were excluded for either
failing to pass two training trials or were not native English speakers,
leaving a total sample of 23 participants. In the five-alternative
condition, 3 participants were excluded for either failing to pass two
training trials or were not native English speakers, leaving a total
sample of 27.

@@

Participants were presented a target scalar term from our original
entailment set embedded in a sentence such as, ``In a recent restaurant
review someone said they thought they the food was \_\_\_\_," with a
target scalar presented in the blank. Participants were then asked to
generate plausible alternatives by responding to the question, ``If
they'd felt differently about the food, what other words could they have
used instead of \_\_\_\_\_?'' They were prompted to generate three
unique alternatives.

@@

Experiment 3 was conducted to measure pragmatic judgments
\(p_{L_1}(m \mid u)\) for five pairs of scalar items taken from Tiel
(2014). We include two conditions in Experiment 3. In the
two-alternative entailment condition, participants made judgments for
items included in the entailment scales. In the four-alternative
condition, participants made pragmatic judgments for the entialment
items and also the top two alternatives elicited for each scale in
Experiment 2. Running two pragmatic judgment conditions allowed us to
rule out the potential effects of having a larger set of alternatives
during the pragmatic judgment elicitation and also provided two sets of
human judgments to compare with model predictions.
\footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

We recruited 100 participants from AMT, 50 for each condition. Data for
9 participants in the two-alternative condition were excluded after
participants either failed to pass two training trials or reported a
non-English native language, leaving a total sample of 41 participants.
In the four-alternative condition, data from 7 participants was thrown
out after participants either failed to pass two training trials or were
not native English speakers, leaving a total sample of 43 participants.

@@

To test whether there were between experiment differences in pragmatic
judgments, we ran a mixed effects model, regressing pragmatic judgements
on scale and experiment with subject and word level random effects.
Results indicate there were no significant differences between
Experiment 3a and 3b for \(b =\) 0.05, \(t(\) 150.4 \() =\) 1.04,
\(p =\) 0.3 and the addition of our experiment predictor did not
significantly improve model fit when compared to a model without the
experiment variable using ANOVA \(\chi^2(\) 1 \() =\) 1.13, \(p =\)
0.29.

@@

Using literal semantic data from Experiment 1 we conducted three
simulations with our model. Each simulation used the specific literal
semantic data to specify the scale representation available to our
model. The ``entailment'' model used only the original pair of scalar
items pulled from van Tiel (2014). These data were measured in
Experiment 1a. The ``Top two'' model extended the original set of
alternatives with the top two alternatives generated in Experiment 2.
These data were measured in Experiment 3a. The ``Full'' model included
the full set of alternatives, including a neutral valenced alternative.
These data were measured in Experiment 4.

>>>>

\[ p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)\]

@@

\[p_{S_1}(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}\]

@@

In each condition we recruited 30 participants from Amazon Mechanical
Turk (AMT). In the two-alternative condition, 16 participants were
excluded
\footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials. We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,c}
for either failing to pass two training trails or were not native
English speakers, leaving a total sample of 14 participants. In the
four-alternative condition, 7 participants were excluded for either
failing to pass two training trials or were not native English speakers,
leaving a total sample of 23 participants. In the five-alternative
condition, 3 participants were excluded for either failing to pass two
training trials or were not native English speakers, leaving a total
sample of 27.

@@

Participants were presented a target scalar term from our original
entailment set embedded in a sentence such as, ``In a recent restaurant
review someone said they thought they the food was \_\_\_\_," with a
target scalar presented in the blank. Participants were then asked to
generate plausible alternatives by responding to the question, ``If
they'd felt differently about the food, what other words could they have
used instead of \_\_\_\_?" They were prompted to generate three unique
alternatives.

@@

Experiment 3 was conducted to measure pragmatic judgments
\(p_{L_1}(m \mid u)\) for five pairs of scalar items taken from Tiel
(2014). We include two conditions in Experiment 3. In the
two-alternative condition, participants made judgments for items
included in the entailment scales. In the four-alternative condition,
participants made judgments for the entialment items and also the top
two alternatives elicited for each scale in Experiment 2. Running two
pragmatic judgment conditions allowed us to rule out the potential
effects of having a larger set of alternatives during the pragmatic
judgment elicitation and also provided two sets of human judgments to
compare with model predictions.
\footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

We recruited 100 participants from AMT, 50 for each condition. Data for
9 participants was excluded after participants either failed to pass two
training trials or were non-native English speakers, leaving a total
sample of 41 participants. In the four-alternative condition, data from
7 participants was excluded after participants either failed to pass two
training trials or were not native English speakers, leaving a total
sample of 43 participants.

@@

To test whether there were between experiment differences in pragmatic
judgments, we ran a mixed effects model, regressing pragmatic judgements
on scale and experiment with subject and word level random effects.
Results indicate there were no significant differences between
Experiment 3a and 3b for \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\)
0.3 and the addition of our experiment predictor did not significantly
improve model fit when compared to a model without the experiment
variable using ANOVA \(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.

@@

Using literal semantic data from Experiments 1a,b,c we conducted three
simulations with our model. Each simulation used the specific literal
semantic data to specify the scale representation available to our
model. The ``entailment'' model used only the original pair of scalar
items pulled from van Tiel (2014). These data were measured in
Experiment 1a. The ``Top two'' model extended the original set of
alternatives with the top two alternatives generated in Experiment 2.
These data were measured in Experiment 3a. The ``Full'' model included
the full set of alternatives, including a neutral valenced alternative.
These data were measured in Experiment 4.
